Comparing R packages for calculation of persistent homology

### 2020-01-31 tdabench-paper/tdabench.Rmd
added narrative for torus figure
revised torus figure caption

Computing persistent homology of a canonical torus grants quick insight into efficiency of each library (Figure \ref{fig:tor}).

\begin{figure}
  \centering
  \includegraphics[height=2.5in]{../Figures/Final_Figures/fig1.png}
  \caption{Comparison of Rips complex persistent homology calculation runtimes across R packages for a torus. The x-axis represents the number of points in a 3D torus point cloud, and y-axis represents average run time. Each library that calculated the Rips complex is differentiated by point color. All calculations calculated up to two dimensional features. Average runtime is presented as mean +/- standard deviation over 10 iterations. ALl three Rips libraries exhibit a polynomial time growth for these parameters. Further details about regression parameters is found in supplemental material on the paper Github. Some libraries are not calculated for all points due to computational limitations, which are described more in the Computational Limitations section.}
\label{fig:tor}
\end{figure}

>>>>

Computing persistent homology of a canonical torus grants quick insight into efficiency of each library (Figure \ref{fig:tor}).
Dionysus exhibits the longest average runtime, and, although Ripser and GUDHI have similar runtimes for smaller point clouds, as the number of points increases Ripser eventually has a significant lead.

\begin{figure}
  \centering
  \includegraphics[height=2.5in]{../Figures/Final_Figures/fig1.png}
  \caption{\textbf{Calculating persistent homology of a torus with three TDA libraries.}
  Average runtime (mean $\pm$ SD) for each TDA library (denoted by color) is plotted against point cloud size.
  Homological features up to 2 dimensions were calculated.
  Time complexity follows a power law for all three libraries (see GitHub repo for regression details).
  Although the libraries have similar runtimes for smaller point clouds, Dionysus has a clear disadvantage when the number of points exceeds 100.
  When the number of points exceeds 200, Ripser has a clear advantage over GUDHI, which maintains its advantage over Dionysus.
  }
\label{fig:tor}
\end{figure}
